Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-06-01 paper.tex
Add BMRC acks
Closes #62

\section{Data Availability}
The source code for \texttt{sc2ts} and notebooks and code used to produce the
results described here available on GitHub
at \url{https://github.com/jeromekelleher/sc2ts/}
and \url{https://github.com/jeromekelleher/sc2ts-paper/}.

>>>>

Computation used the Oxford Biomedical Research Computing (BMRC) facility, a
joint development between the Wellcome Centre for Human Genetics and the Big
Data Institute supported by Health Data Research UK and the NIHR Oxford
Biomedical Research Centre. The views expressed are those of the author(s) and
not necessarily those of the NHS, the NIHR or the Department of Health.

\section{Data Availability}
The source code for \texttt{sc2ts} and notebooks and code used to produce the
results described here available on GitHub:
\begin{itemize}
\item \url{https://github.com/jeromekelleher/sc2ts/}
\item\url{https://github.com/jeromekelleher/sc2ts-paper/}
\end{itemize}
